Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Change nomenclature of valve types.

%Due to evolving developments in our group, two types of valves are considered, as will be elaborated in \autoref{sec:results-discussions}.

In the present analysis, two types of valves are considered. In the first approach, called \emph{Type B valves}, the  model proposed in Ref.~\cite{bib:cardoso16_trans} is used, assuming that the individual consumption of each valve is independent of frequency and blow fraction. The valve power  $\wvalve$ can be computed as:

\colorbox{yellow}{da mesma forma, o trabalho \cite{bib:cardoso16_trans} tem que constar da revisao bibliografica...}

\colorbox{yellow}{fica estranho o \textbf{primeiro} approach ser Type B e o \textbf{segundo} ser Type A...}

@@

In the second approach, \emph{Type A} valves are used, with  nominal power lower in magnitude but which depends on frequency and blow fraction. For these valves, the valve power was experimentally correlated as:

@@

At the first stage of the present analysis, the instantaneous and rectified cosine profiles are compared considering a single-layer regenerator  without casing losses, using Type B valves. The parameters used in all simulations are presented in \autoref{tab:params-cobem}.

@@

The simulations in this section also use multilayer regenerators. A summary of all parameters adopted in this section, including the Curie temperatures and volumetric fractions (relative to the length of the bed) of each layer is presented in \autoref{tab:params-ramp}.

>>>>

% Type R = Type B (BuRkert)
% Type S = Type A (ASco)

In the present analysis, two types of valves are considered. In the first approach, called \emph{Type R valves}, the  model proposed in \cite{bib:cardoso16_trans} is used, assuming that the individual consumption of each valve is independent of frequency and blow fraction. The valve power  $\wvalve$ can be computed as:

@@

In the second approach, \emph{Type S} valves are used, with  nominal power lower in magnitude but which depends on frequency and blow fraction. For these valves, the valve power was experimentally correlated as:

@@

At the first stage of the present analysis, the instantaneous and rectified cosine profiles are compared considering a single-layer regenerator  without casing losses, using Type R valves. The parameters used in all simulations are presented in \autoref{tab:params-cobem}.

@@

The simulations in this section also use multilayer regenerators. A summary of all parameters adopted in this section, including the Curie temperatures and volumetric fractions (relative to the length of the bed) of each layer is presented in \autoref{tab:params-ramp}. In addition, in the following results, Type S valves are used, with valve power calculated by \autoref{eq:198}.
